### 2014-03-25 Pero_Transcriptome.tex
tues AM

Animals

>>>>

To begin to understand how genes may underlie desert adaptation, I collected ~15 individuals from a single population \textit{P. eremicus} over a two year time period (2012-2013). These individuals were captured in live traps, then euthanized using isoflurane overdose and decapitation. Immediately post-mortem, the abdominal and pelvis organs were removed, cut in half (in the case of kidney), placed in RNAlater and flash frozen in liquid Nitrogen. Removal of the brain, with similar preservation techniques followed that. Time from euthanasia to removal of all organs never exceeded five minutes. Samples were transferred to a -80C freezer at a later date. These procedures were approved by the University of California Berkeley Animal Care and Use Committee and follow guidelines established by the American Society of Mammalogy for the use of wild animals in research \cite{Sikes:2011dz}.
